A comparison of design-based and model-based approaches for finite population spatial data -- Supporting information.

### 2022-06-11 inst/manuscript/supporting.tex
minor review updates
minor updates
minor updates pre zenodo

\usepackage{lineno} % add
  \linenumbers % turns line numbering on

@@

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

@@

      \address[USEPA]{United States Environmental Protection Agency, 200 SW 35th St,
Corvallis, Oregon, 97333}
    \address[STLAW]{Saint Lawrence University Department of Mathematics, Computer Science,
and Statistics, 23 Romoda Drive, Canton, New York, 13617}
    \address[OSU]{Oregon State University Department of Statistics, 239 Weniger Hall,
Corvallis, Oregon, 97331}
    \address[NOAA]{Marine Mammal Laboratory, Alaska Fisheries Science Center, National
Oceanic and Atmospheric Administration, Seattle, Washington, 98115}
      \cortext[1]{Corresponding Author: Michael Dumelle (Dumelle.Michael@epa.gov)}

@@

Approach & Layout & Response & DRE\% & n & MB & RMSE & Coverage \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 1.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 2.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 3.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 4.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 5.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 6.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 7.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 8.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 9.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 10.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 11.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 12.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 13.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 14.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 15.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 16.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 17.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 18.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 19.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 20.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 21.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 22.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 23.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 24.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 25.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 26.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 27.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 28.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 29.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 30.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 31.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 32.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 33.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 34.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 35.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 36.} 

@@

\begin{table}[ht]
\centering
\scalebox{0.8}{
\begin{tabular}{llrrrr}
  \hline
Approach & Response & n & MB & RMSE & Coverage \\ 
  \hline
SRS-DB & Hg ppb & 50 & 0.2539 & 12.9467 & 0.9215 \\ 
  SRS-MB & Hg ppb & 50 & 0.0573 & 11.3760 & 0.9020 \\ 
  GRTS-DB & Hg ppb & 50 & -0.1880 & 10.5558 & 0.8970 \\ 
  GRTS-MB & Hg ppb & 50 & -0.5604 & 10.4434 & 0.9070 \\ 
   \hline
\end{tabular}
}
\caption{Sampling-inference combination (Approach), response type (Response), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in a data application scenario 1.} 
\end{table}
\begin{table}[ht]
\centering
\scalebox{0.8}{
\begin{tabular}{llrrrr}
  \hline
Approach & Response & n & MB & RMSE & Coverage \\ 
  \hline
SRS-DB & ZMMI & 50 & 0.0461 & 2.4502 & 0.9440 \\ 
  SRS-MB & ZMMI & 50 & 0.0000 & 2.1477 & 0.9395 \\ 
  GRTS-DB & ZMMI & 50 & -0.0047 & 1.9953 & 0.9210 \\ 
  GRTS-MB & ZMMI & 50 & -0.1191 & 1.9608 & 0.9355 \\ 
   \hline
\end{tabular}
}
\caption{Sampling-inference combination (Approach), response type (Response), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in a data application scenario 2.} 
\end{table}
\begin{table}[ht]
\centering
\scalebox{0.8}{
\begin{tabular}{llrrrr}
  \hline
Approach & Response & n & MB & RMSE & Coverage \\ 
  \hline
SRS-DB & Hg ppb & 100 & -0.1390 & 8.9667 & 0.9290 \\ 
  SRS-MB & Hg ppb & 100 & -0.4213 & 7.4820 & 0.9190 \\ 
  GRTS-DB & Hg ppb & 100 & 0.0075 & 7.1415 & 0.9045 \\ 
  GRTS-MB & Hg ppb & 100 & -0.4156 & 7.0344 & 0.9230 \\ 
   \hline
\end{tabular}
}
\caption{Sampling-inference combination (Approach), response type (Response), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in a data application scenario 3.} 
\end{table}
\begin{table}[ht]
\centering
\scalebox{0.8}{
\begin{tabular}{llrrrr}
  \hline
Approach & Response & n & MB & RMSE & Coverage \\ 
  \hline
SRS-DB & ZMMI & 100 & -0.0541 & 1.6901 & 0.9460 \\ 
  SRS-MB & ZMMI & 100 & -0.0942 & 1.3920 & 0.9445 \\ 
  GRTS-DB & ZMMI & 100 & -0.0066 & 1.3219 & 0.9205 \\ 
  GRTS-MB & ZMMI & 100 & -0.0968 & 1.2958 & 0.9450 \\ 
   \hline
\end{tabular}
}
\caption{Sampling-inference combination (Approach), response type (Response), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in a data application scenario 4.} 
\end{table}
\begin{table}[ht]
\centering
\scalebox{0.8}{
\begin{tabular}{llrrrr}
  \hline
Approach & Response & n & MB & RMSE & Coverage \\ 
  \hline
SRS-DB & Hg ppb & 200 & -0.0876 & 5.9176 & 0.9450 \\ 
  SRS-MB & Hg ppb & 200 & -0.1775 & 4.6970 & 0.9400 \\ 
  GRTS-DB & Hg ppb & 200 & -0.0538 & 4.5051 & 0.9325 \\ 
  GRTS-MB & Hg ppb & 200 & -0.2762 & 4.3998 & 0.9410 \\ 
   \hline
\end{tabular}
}
\caption{Sampling-inference combination (Approach), response type (Response), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in a data application scenario 5.} 
\end{table}
\begin{table}[ht]
\centering
\scalebox{0.8}{
\begin{tabular}{llrrrr}
  \hline
Approach & Response & n & MB & RMSE & Coverage \\ 
  \hline
SRS-DB & ZMMI & 200 & -0.0093 & 1.1311 & 0.9455 \\ 
  SRS-MB & ZMMI & 200 & -0.0736 & 0.9090 & 0.9450 \\ 
  GRTS-DB & ZMMI & 200 & 0.0193 & 0.8524 & 0.9460 \\ 
  GRTS-MB & ZMMI & 200 & -0.0311 & 0.8280 & 0.9450 \\ 
   \hline
\end{tabular}
}
\caption{Sampling-inference combination (Approach), response type (Response), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in a data application scenario 6.} 
\end{table}

>>>>

\usepackage{lineno} % add
  \linenumbers % turns line numbering on
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

@@

% Pandoc citation processing

% Pandoc header

@@

      \address[USEPA]{United States Environmental Protection Agency, 200
SW 35th St, Corvallis, Oregon, 97333}
    \address[STLAW]{St.~Lawrence University Department of Mathematics,
Computer Science, and Statistics, 23 Romoda Drive, Canton, New York,
13617}
    \address[OSU]{Oregon State University Department of Statistics, 239
Weniger Hall, Corvallis, Oregon, 97331}
    \address[NOAA]{Marine Mammal Laboratory, Alaska Fisheries Science
Center, National Oceanic and Atmospheric Administration, Seattle,
Washington, 98115}
      \cortext[1]{Corresponding Author: Michael Dumelle
(Dumelle.Michael@epa.gov)}

@@

Approach & Layout & Response & DRE\% & n & MBias & RMSE & Coverage \\ 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 1.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 2.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 3.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 4.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 5.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 6.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 7.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 8.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 9.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 10.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 11.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 12.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 13.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 14.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 15.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 16.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 17.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 18.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 19.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 20.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 21.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 22.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 23.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 24.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 25.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 26.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 27.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 28.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 29.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 30.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 31.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 32.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 33.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 34.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 35.} 

@@

\caption{Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in simulation scenario 36.} 

@@

\begin{table}[ht]
\centering
\scalebox{0.8}{
\begin{tabular}{llrrrr}
  \hline
Approach & Response & n & MBias & RMSE & Coverage \\ 
  \hline
SRS-DB & Hg ppb & 50 & 0.2539 & 12.9467 & 0.9215 \\ 
  SRS-MB & Hg ppb & 50 & 0.0573 & 11.3760 & 0.9020 \\ 
  GRTS-DB & Hg ppb & 50 & -0.1880 & 10.5558 & 0.8970 \\ 
  GRTS-MB & Hg ppb & 50 & -0.5604 & 10.4434 & 0.9070 \\ 
   \hline
\end{tabular}
}
\caption{Sampling-inference combination (Approach), response type (Response), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in a data application scenario 1.} 
\end{table}
\begin{table}[ht]
\centering
\scalebox{0.8}{
\begin{tabular}{llrrrr}
  \hline
Approach & Response & n & MBias & RMSE & Coverage \\ 
  \hline
SRS-DB & ZMMI & 50 & 0.0461 & 2.4502 & 0.9440 \\ 
  SRS-MB & ZMMI & 50 & 0.0000 & 2.1477 & 0.9395 \\ 
  GRTS-DB & ZMMI & 50 & -0.0047 & 1.9953 & 0.9210 \\ 
  GRTS-MB & ZMMI & 50 & -0.1191 & 1.9608 & 0.9355 \\ 
   \hline
\end{tabular}
}
\caption{Sampling-inference combination (Approach), response type (Response), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in a data application scenario 2.} 
\end{table}
\begin{table}[ht]
\centering
\scalebox{0.8}{
\begin{tabular}{llrrrr}
  \hline
Approach & Response & n & MBias & RMSE & Coverage \\ 
  \hline
SRS-DB & Hg ppb & 100 & -0.1390 & 8.9667 & 0.9290 \\ 
  SRS-MB & Hg ppb & 100 & -0.4213 & 7.4820 & 0.9190 \\ 
  GRTS-DB & Hg ppb & 100 & 0.0075 & 7.1415 & 0.9045 \\ 
  GRTS-MB & Hg ppb & 100 & -0.4156 & 7.0344 & 0.9230 \\ 
   \hline
\end{tabular}
}
\caption{Sampling-inference combination (Approach), response type (Response), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in a data application scenario 3.} 
\end{table}
\begin{table}[ht]
\centering
\scalebox{0.8}{
\begin{tabular}{llrrrr}
  \hline
Approach & Response & n & MBias & RMSE & Coverage \\ 
  \hline
SRS-DB & ZMMI & 100 & -0.0541 & 1.6901 & 0.9460 \\ 
  SRS-MB & ZMMI & 100 & -0.0942 & 1.3920 & 0.9445 \\ 
  GRTS-DB & ZMMI & 100 & -0.0066 & 1.3219 & 0.9205 \\ 
  GRTS-MB & ZMMI & 100 & -0.0968 & 1.2958 & 0.9450 \\ 
   \hline
\end{tabular}
}
\caption{Sampling-inference combination (Approach), response type (Response), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in a data application scenario 4.} 
\end{table}
\begin{table}[ht]
\centering
\scalebox{0.8}{
\begin{tabular}{llrrrr}
  \hline
Approach & Response & n & MBias & RMSE & Coverage \\ 
  \hline
SRS-DB & Hg ppb & 200 & -0.0876 & 5.9176 & 0.9450 \\ 
  SRS-MB & Hg ppb & 200 & -0.1775 & 4.6970 & 0.9400 \\ 
  GRTS-DB & Hg ppb & 200 & -0.0538 & 4.5051 & 0.9325 \\ 
  GRTS-MB & Hg ppb & 200 & -0.2762 & 4.3998 & 0.9410 \\ 
   \hline
\end{tabular}
}
\caption{Sampling-inference combination (Approach), response type (Response), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in a data application scenario 5.} 
\end{table}
\begin{table}[ht]
\centering
\scalebox{0.8}{
\begin{tabular}{llrrrr}
  \hline
Approach & Response & n & MBias & RMSE & Coverage \\ 
  \hline
SRS-DB & ZMMI & 200 & -0.0093 & 1.1311 & 0.9455 \\ 
  SRS-MB & ZMMI & 200 & -0.0736 & 0.9090 & 0.9450 \\ 
  GRTS-DB & ZMMI & 200 & 0.0193 & 0.8524 & 0.9460 \\ 
  GRTS-MB & ZMMI & 200 & -0.0311 & 0.8280 & 0.9450 \\ 
   \hline
\end{tabular}
}
\caption{Sampling-inference combination (Approach), response type (Response), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\% interval coverage (Coverage) in a data application scenario 6.} 
\end{table}
